Comparison of dimensionality reduction schemes for parallel global optimization algorithms \thanks{The study was supported by the Russian Science Foundation, project No 16-11- 10150}

### 2018-05-27 2018/RSD/MultiEvolvents/RSD.tex
RSD: fix review comments

Many methods destined to solving the problems of the class specified above reduce the solving
of a multidimensional problem to solving the one-dimensional subproblems implicitly (see, for
example, the methods of diagonal partitions \cite{Sergeyev2006,SergeyevKvasov2015} or
simplicial partitions \cite{Zilinskas2008,Zilinskas2014}). In the present work, we will use the
approach developed in Lobachevsky State University of Nizhni Novgorod based on the idea of
the dimensionality reduction with the use of Peano space-filling curves $y(x)$ mapping the
interval $[0,1]$ of the real axis onto an $n$-dimensional cube continuously and unambiguously.

@@

@@

\bibitem{Sergeyev2006}
Sergeyev, Ya.D., Kvasov, D.E.: \emph{Global search based on efficient diagonal partitions and a set
of Lipschitz constants}. SIAM J. Optim \textbf{16(3)}, 910--937 (2006)

@@

\bibitem{Zilinskas2008}
\v Zilinskas, J.: \emph{Branch and bound with simplicial partitions for global optimization.} Math.
Model. Anal. \textbf{13(1)}, 145--159 (2008)

\bibitem{Zilinskas2014}
Paulavi\v cius, R., \v Zilinskas, J.: \emph{Simplicial Lipschitz optimization without the Lipschitz
constant.} J. Glob. Optim. \textbf{59(1)}, 23-40 (2014)

@@

>>>>

Many methods destined to solving the problems of the class specified above reduce the solving
of a multidimensional problem to solving the one-dimensional subproblems implicitly (see, for
example, the methods of diagonal partitions \cite{SergeyevKvasov2015} or
simplicial partitions \cite{Zilinskas2014}). In the present work, we will use the
approach developed in Lobachevsky State University of Nizhni Novgorod based on the idea of
the dimensionality reduction with the use of Peano space-filling curves $y(x)$ mapping the
interval $[0,1]$ of the real axis onto an $n$-dimensional cube continuously and unambiguously.

@@

The numerical experiments, the results of which are presented in \cite{GergelLebedev,GergelSidorov} demonstrate that the method, at least, is not worse than the well-known global optimization algorithms DIRECT \cite{Jones} and DIRECT\textit{l} \cite{Gablonsky}, and even overcome these ones with respect to some parameters.

@@

%\bibitem{Sergeyev2006}
%Sergeyev, Ya.D., Kvasov, D.E.: \emph{Global search based on efficient diagonal partitions and a set
%of Lipschitz constants}. SIAM J. Optim \textbf{16(3)}, 910--937 (2006)

@@

%\bibitem{Zilinskas2008}
%\v Zilinskas, J.: \emph{Branch and bound with simplicial partitions for global optimization.} Math.
%Model. Anal. \textbf{13(1)}, 145--159 (2008)

\bibitem{Zilinskas2014}
Paulavi\v cius, R., \v Zilinskas, J.: \emph{Simplicial Lipschitz optimization without the Lipschitz
constant.} J. Glob. Optim. \textbf{59(1)}, 23--40 (2014)

@@

\bibitem{GergelLebedev}
Gergel V. and Lebedev I. \emph{Heterogeneous Parallel Computations for Solving Global Optimization Problems.} Proc. Comput. Science \textbf{66}, pp. 53--62 (2015)

\bibitem{GergelSidorov}
Gergel V., Sidorov S. \emph{A Two-Level Parallel Global Search Algorithm for Solution of Computationally Intensive Multiextremal Optimization Problems.} {Lect. Notes Comput. Science} \textbf{9251}, pp. 505--515 (2015)
